\begin{frame}{Forward Euler Scheme for ODEs}{Definition}
    Suppose that we have an ODE of the form
    \begin{equation}
        dX(t) = f(X(t), t)dt, \quad X(0) = X_0. \label{eq:ode}
    \end{equation}
    Then it could be numerically solved by the following finite difference scheme:
    \begin{equation}
        X_{n+1} = X_n + f(t_n, X_n)h_n, \label{Euler:ODE}
    \end{equation}
    where $t_n = \sum_{k=1}^n h_n, t_0 = 0$ is a grid. 
\end{frame}

\begin{frame}{Forward Euler Scheme for ODEs}{Global truncation error}
    \begin{lemma}
        Let the solution of \eqref{eq:ode} have an $M$-bounded second derivative and let $f$ be $L$-Lipshitz continious in its second argument. Then the global truncation error of the mesh solution \eqref{Euler:ODE} is
        \begin{equation}
            \left|X(T) - X_N\right| \leq \frac{hM}{2L}\left(e^{LT} - 1\right) = O(h).
        \end{equation}
    \end{lemma}
\end{frame}

\begin{frame}{Euler-Maruyama Scheme for SDEs}{Definition}
    Suppose we have a diffusion of the form 
    \begin{equation*}
        dX(t) = f(X(t), t)dt + \sigma(X(t), t)dW(t), \quad X(0) = X_0.
    \end{equation*}
    Then it could be numerically solved by the following finite difference scheme:
    \begin{equation}
        X_{n+1} = X_n + f(t_n, X_n)h_n + \sigma(t_n, X_n) \sqrt{h_n} Z_n, \label{Euler:SDE}
    \end{equation}
    where $(Z_n)_{n=1, 2, \dots}$ is a sample of standard normal random variables, and $t_n = \sum_{k=1}^n h_n, t_0 = 0$ is a grid.
    The same method could be generalized for the two-factor Gaussian diffusions. Further we assume
    that $(t_i)_{i = 0, 1, \dots}$ is a uniform grid with $t_i = ih$.
\end{frame}

\begin{frame}{Euler-Maruyama Scheme for SDEs}{Strong and weak convergence as a global truncation error analogue}
    \begin{definition}
        Let $\hat X^n(t)$ be a piecewise mesh approximation of an SDE solution $X(t)$ (we assume that there exists a unique strong solution). 
        Then a scheme is said to have a strong convergence of order $p$ if 
        \begin{equation}
            \E\left[\left|\hat X^n(T) - X(T)\right|\right] \leq Ch^p, \quad n \to \infty.
        \end{equation}
        A scheme is said to have a weak convergence of order $p$ if for any polynomial $f: \R \to \R$ we have
        \begin{equation}
            \left|\E\left[f(\hat X^n(T))\right] - \E\left[f(X(T))\right]\right| \leq Ch^p, \quad n \to \infty.
        \end{equation}
    \end{definition}
    
\end{frame}

\begin{frame}{Euler-Maruyama Scheme for SDEs}{Strong and weak convergence as a global truncation error analogue}
    \begin{theorem}
        Under some technical assumptions the Euler-Maruyama scheme \eqref{Euler:SDE} has a strong convergence of order $1/2$ and a weak convergence of order $1$.
    \end{theorem}

    \begin{nb}
        Since our goal is to approximate $\E\left[h(X)\right]$ with a given accuracy and the least possible number of simulations, we need to compare the weak convergence rate between the methods.
    \end{nb}
\end{frame}

\begin{frame}{Euler Scheme for the Heston Model}{Classical Euler-Maruyama Scheme}
    Suppose we have the Heston model \eqref{Heston:price} -- \eqref{Heston:variance}. Then it could be numerically solved by the following finite difference scheme:
    \begin{align}
        S_{n+1} & = S_n + \mu S_n h_n + \sqrt{v_n} S_n \sqrt{h_n} Z_{1,n}, \label{Euler:Heston:price}\\
        v_{n+1} & = v_n + \left(\delta^2 - 2\beta v_n\right) h_n + \sigma \sqrt{v_n} \sqrt{h_n} Z_{2,n}, \label{Euler:Heston:variance}
    \end{align}
    where $(Z_{1,n})_{n=1, 2, \dots}$ and $(Z_{2,n})_{n=1, 2, \dots}$ are $\rho$-correlated samples of standard normal random variables, and $t_n = \sum_{k=1}^n h_n$ is a grid.
\end{frame}

\begin{frame}{Euler Scheme for the Heston Model}{Modified Euler-Maruyama Scheme}
    But we have a problem: during simulation of the Heston model using Euler method $S_{t_n}$ and $v_{t_n}$ could be negative. How do we deal with this inconvenience?
    Let us introduce the log-prices
    \begin{equation}
        X(t) := \log\frac{S(t)}{S(0)}.
    \end{equation}
\end{frame}

\begin{frame}{Euler Scheme for the Heston Model}{Modified Euler-Maruyama Scheme}
    
    We take the positive part of the variance:
    \begin{align}
        X_{n+1} & = X_n + (\mu - 0.5 v_n^+)h_n + \sqrt{v_n^+} X_n \sqrt{h_n} Z_{1,n}, \label{Euler:Heston:price:posmod}\\
        v_{n+1} & = v_n + \left(\delta^2 - 2\beta v_n^+\right) h_n + \sigma \sqrt{v_n^+} \sqrt{h_n} Z_{2,n}, \label{Euler:Heston:variance:posmod}
    \end{align}
    and then we take the exponential of the log-prices:
    \begin{equation}
        S_{n} = S_0 e^{X_{n}}.
    \end{equation}
    
    However, the scheme is not accurate, since we ignore the $dZ_idZ_j$ terms in the It\^o-Taylor series approximation.
\end{frame}